Integration of 75MW Solar PV Plant: Transmission System Design Analysis

### 2024-12-07 paper.tex
updates with correct parameters

The optimal solution will minimize total cost, calculated as the construction costs minus any savings from reduced system losses over a 5-year period at \$60/MWh. Construction costs include both fixed components (\$1.25M for 138 kV or \$750k for 69 kV lines) and variable costs based on distance and conductor type. If 138 kV is utilized, additional costs include substation upgrades (\$900k per substation) and necessary transformers (\$1.5M for 101 MVA or \$1.8M for 168 MVA). The solution must resolve existing contingency violations, particularly the overloads observed in the OAK69-BUCKEYE69-APPLE69 corridor, while ensuring reliable operation both when the solar plant is at full output and when it is offline.
\subsection{Transmission Line Parameters}
A note on how to input transmission line parameters into PowerWorld is in order. Table A.4 in the text gives resistance in ohms per conductor per mile for 50$^\circ$C at 60Hz as well as series inductance (ohms/mile/conductor for 1 foot spacing) and shunt capacitance (S/mile/conductor for 1 foot spacing). Resistance pulled from Table A.4 can be used directly in the "Calculate Impedances" dialog box in PowerWorld. But for 69kV lines, the three phases are spaced 2m apart and 4m apart for 138kV lines. We need a way to convert the 1-foot spacing parameters appropriately. Assuming equilateral spacing of lines, Equation 4.5.9 in the text suggests a simple way to adjust series per-mile impedance from the table:
\begin{flalign}
	X_{2m} &= X_{1ft}\cdot\frac{\ln\left(\frac{2\times3.28}{\text{GMR}}\right)}{\ln\left(\frac{1}{\text{GMR}}\right)}
\end{flalign}
where GMR comes from the same table for the conductor of interest. We calculate shunt susceptance manually using values given in the table:
\begin{flalign}
	B_{2m} & = \frac{2\pi\epsilon}{\ln(D/r)}
\end{flalign}
where $r$ is the conductor's outer radius. Though these are stranded conductors, we treat them as solid since the associated error is small. Note that we multiply this value by 3 for 3 phases.

Table \ref{tab:tl_params} shows parameters for the 69kV lines which go into PowerWorld's Impedance Calculator. We do not include the 138kV lines for reasons explained in the next section.
\begin{table}
	\begin{tabular}{|l|c|c|c|}
		\hline
		Parameter & Rook & Crow & Condor \\
		\hline
		R ($\Omega$/mile) & 0.1688 & 0.1482 & 0.1378 \\
		X ($\Omega$/mile) & 0.6421 & 0.6352 & 0.6326 \\
		B (S/mile) & $16.15\times10^{-6}$ & $16.30\times10^{-6}$ & $16.44\times10^{-6}$ \\
		\hline
	\end{tabular}
	\vspace{0.5em}
	\caption{Transmission Line Parameters at 60 Hz, 2m Spacing}
	\label{tab:tl_params}
\end{table}
\subsection{Candidate Solutions}
Table \ref{tab:all_conn} shows all possible NEWSOLAR connections to the network, given the provided set of right-of-way paths available to us. The cost of 138kV lines and transformers suggests we can eliminate any solution involving those lines; we will connect NEWSOLAR exclusively with 69kV lines unless we are unable to solve potential contingency violations. The approach here is to start with the solution involving least total line distance (case 1). We move to solutions involving longer connections only if we run into contingency violations. Further, we use the least expensive conductors to start and upgrade only if needed. 
\begin{table}[h]
	\centering
	\begin{tabular}{|c|l|c|}
		\hline
		\textbf{Case number} & \textbf{Destination buses} & \textbf{Total distance} \\
		\hline
		1 & BK69, AP69 & 12 \\
		2 & BK69, OAK69 & 19 \\
		3 & BK69, OAK138 & 19 \\
		4 & AP69, OAK69 & 19 \\
		5 & AP69, OAK138 & 19 \\
		6 & BK69, PIINE69 & 20 \\
		7 & BK69, PINE138 & 20 \\
		8 & AP69, PINE69 & 20 \\
		9 & AP69, PINE138 & 20 \\
		10 & BK69, MP69 & 21 \\
		11 & AP69, MP69 & 21 \\
		12 & OAK69, PINE69 & 27 \\
		13 & OAK69, PINE138 & 27 \\
		14 & OAK138, PINE69 & 27 \\
		15 & OAK138, PINE138 & 27 \\
		16 & OAK69, MP69 & 28 \\
		17 & OAK138, MP69 & 28 \\
		18 & PINE69, MP69 & 29 \\
		19 & PINE138, MP69 & 29 \\
		\hline
	\end{tabular}
	\vspace{0.5em}
	\caption{Possible NEWSOLAR Connections}
	\label{tab:all_conn}
\end{table}
We started with case 1: maintain NEWSOLAR at 69kV with connections to BUCKEYE and APPLE using Rook 770A conductors.

First we attempted to maintain NEWSOLAR at 69kV with new connections to BUCKEYE and APPLE using Condor 900A/107.5MVA conductors. We selected those stations because of their proximity to NEWSOLAR (only 6km each). We upgraded the OAK69-BUCKEYE69 and BUCKEYE69-APPLE69 lines to the highest-rated available 69kV conductor (Condor at 900A). However, contingency analysis revealed voltage violations at OAK138, dropping to 0.939 per unit when the OAK345-OAK138 transformer is opened. This suggests a need for stronger integration with the 138kV network.

Next we installed a 138kV bus at NEWSOLAR with a 138/69kV transformer connecting it to the 69kV bus. Since voltage dropped too low at OAK in the previous design, we connected NEWSOLAR138 to OAK138 using Cardinal 1010A/241.4MVA lines. Since 138kV lines are significantly more expensive than 69kV, we kept the 69kV connection to PINE69. We found a slight overcurrent contingency violation on the OAK69-BUCKEYE69 line when PINE-APPLE is open, so we upgraded it to the 900A Condor lines. With this new configuration there are no contingency violations.

PowerWorld's Case Summary for this configuration shows losses of 10.6MW, a 0.1MW decrease from the base scenario. That will slightly offset upgrade costs from power saving over five years. Contingency analysis showed no violations with this configuration, so we now examine the cost of this approach. Table \ref{tab:cost_breakdown_option1} shows the breakdown of costs incurred, with a total of \$20,927,200.
\begin{table}[h!]
	\centering
	\begin{tabular}{|l|r|}
		\hline
		\textbf{Modification} & \textbf{Cost (\$)} \\ \hline
		\multicolumn{2}{|l|}{\textbf{Replace OAK-BUCKEYE (69kV Condor)}} \\ 
		\hspace{1em} Fixed Cost & 750,000 \\ 
		\hspace{1em} Variable Cost (\$410,000/km for 8 km) & 3,280,000 \\ 
		\hspace{1em} \textbf{Total} & \textbf{4,030,000} \\ \hline
		\multicolumn{2}{|l|}{\textbf{138-kV Bus/101MVA Transformer}} \\ 
		\hspace{1em} Bus & 900,000 \\ 
		\hspace{1em} Transformer & 1,500,000 \\ 
		\hspace{1em} \textbf{Total} & \textbf{2,400,000} \\ \hline
		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-OAK138 (138kV Cardinal)}} \\ 
		\hspace{1em} Fixed Cost & 1,250,000 \\ 
		\hspace{1em} Variable Cost (\$540,000/km for 13 km) & 7,020,000 \\ 
		\hspace{1em} \textbf{Total} & \textbf{8,270,000} \\ \hline
		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-PINE69 (69kV Condor)}} \\ 
		\hspace{1em} Fixed Cost & 750,000 \\ 
		\hspace{1em} Variable Cost (\$410,000/km for 14 km) & 5,740,000 \\ 
		\hspace{1em} \textbf{Total} & \textbf{6,490,000} \\ \hline
		\textbf{Loss Savings (0.1 MW over 5 years)} & \textbf{-262,800} \\ \hline
		\textbf{Grand Total} & \textbf{20,927,200} \\ \hline
	\end{tabular}
	\vspace{0.5em}
	\caption{Cost Breakdown of Transmission Line and Transformer Upgrades, Including Loss Savings}
	\label{tab:cost_breakdown_option1}
\end{table}

The massive expense of replacing lines seen in Table \ref{tab:cost_breakdown_option1} suggests that loss reduction will not pay for more line upgrades. Next we examine whether there is a better way to connect NEWSOLAR to the grid, perhaps with closer stations.
\section{Conclusion}
Summary of key findings and recommendations

\begin{thebibliography}{00}
	\bibitem{b1} PowerWorld Corporation, "PowerWorld Simulator Manual," 2024.
	\bibitem{b2} IEEE Standard 1547-2018, "IEEE Standard for Interconnection and Interoperability of Distributed Energy Resources with Associated Electric Power Systems Interfaces."
\end{thebibliography}

\end{document}

>>>>

The optimal solution will minimize total cost, calculated as the construction costs minus any savings from reduced system losses over a 5-year period at \$60/MWh. Construction costs include both fixed components (\$1.25M for 138 kV or \$750k for 69 kV lines) and variable costs based on distance and conductor type. If 138 kV is utilized, additional costs include substation upgrades (\$900k per substation) and necessary transformers (\$1.5M for 101 MVA or \$1.8M for 168 MVA). The solution must resolve existing contingency violations, particularly the overloads observed in the OAK69-BUCKEYE69-APPLE69 corridor, while ensuring reliable operation both when the solar plant is at full output and when it is offline.
\subsection{Transmission Line Parameters}
A note on how to input transmission line parameters into PowerWorld is in order. Table A.4 in the text gives resistance in ohms per conductor per mile for 50$^\circ$C at 60Hz as well as series inductance (ohms/mile/conductor for 1 foot spacing) and shunt capacitance (S/mile/conductor for 1 foot spacing). Resistance pulled from Table A.4 can be used directly in the "Calculate Impedances" dialog box in PowerWorld. But for 69kV lines, the three phases are spaced 2m apart and 4m apart for 138kV lines. We need a way to convert the 1-foot spacing parameters appropriately. Assuming equilateral spacing of lines, Equation 4.5.9 in the text suggests a simple way to adjust series per-mile impedance from the table:
\begin{flalign}
	X_{2m} &= X_{1ft}\cdot\frac{\ln\left(\frac{2\times3.28}{\text{GMR}}\right)}{\ln\left(\frac{1}{\text{GMR}}\right)}
\end{flalign}
where GMR comes from the same table for the conductor of interest.

We calculate shunt susceptance similarly given the 1-foot spacing shunt reactance and outer diameter given in the table:
\begin{flalign}
	B_{2m} & = \frac{\ln(1/r)}{Xc_{1ft}\cdot\ln(2\times3.28/r)}
\end{flalign}
where $r$ is the conductor's outer radius. Though these are stranded conductors, we treat them as solid since the associated error is small. Note that we multiply this value by 3 for 3 phases.

Table \ref{tab:tl_params} shows parameters for the 69kV lines which go into PowerWorld's Impedance Calculator. We do not include the 138kV lines for reasons explained in the next section.
\begin{table}
	\begin{tabular}{|l|c|c|c|}
		\hline
		Parameter & Rook & Crow & Condor \\
		\hline
		R ($\Omega$/mile) & 0.1688 & 0.1482 & 0.1378 \\
		X ($\Omega$/mile) & 0.6421 & 0.6352 & 0.6326 \\
		B (S/mile) & $6.63\times10^{-6}$ & $6.71\times10^{-6}$ & $6.78\times10^{-6}$ \\
		\hline
	\end{tabular}
	\vspace{0.5em}
	\caption{Transmission Line Parameters at 60 Hz, 2m Spacing}
	\label{tab:tl_params}
\end{table}
\subsection{Candidate Solutions}
Table \ref{tab:all_conn} shows all possible NEWSOLAR connections to the network, given the provided set of right-of-way paths available to us. The cost of 138kV lines and transformers suggests we can eliminate any solution involving those lines; we will connect NEWSOLAR exclusively with 69kV lines unless we are unable to solve potential contingency violations.

The approach here is to start with the solution involving least total line distance (case 1). We move to solutions involving longer connections only if we run into contingency violations. Further, we use the least expensive conductors to start and upgrade only if needed. 
\begin{table}[h]
	\centering
	\begin{tabular}{|c|l|c|r|}
		\hline
		\textbf{Case} & \textbf{Destination} & \textbf{Total} & \textbf{Total Cost} \\
		\textbf{number} & \textbf{buses} & \textbf{distance (km)} & \textbf{(M\$)} \\
		\hline
		1 & BK69, AP69 & 12 & 5.94 \\
		2 & BK69, OAK69 & 19 & 8.53 \\
		3 & BK69, OAK138 & 19 & 15.17 \\
		4 & AP69, OAK69 & 19 & 8.53 \\
		5 & AP69, OAK138 & 19 & 15.17 \\
		6 & BK69, PIINE69 & 20 & 8.90 \\
		7 & BK69, PINE138 & 20 & 15.80 \\
		8 & AP69, PINE69 & 20 & 8.90 \\
		9 & AP69, PINE138 & 20 & 15.80 \\
		10 & BK69, MP69 & 21 & 9.27 \\
		11 & AP69, MP69 & 21 & 9.27 \\
		12 & OAK69, PINE69 & 27 & 11.49 \\
		13 & OAK69, PINE138 & 27 & 19.56 \\
		14 & OAK138, PINE69 & 27 & 19.56 \\
		15 & OAK138, PINE138 & 27 & 19.56 \\
		16 & OAK69, MP69 & 28 & 11.86 \\
		17 & OAK138, MP69 & 28 & 20.19 \\
		18 & PINE69, MP69 & 29 & 12.23 \\
		19 & PINE138, MP69 & 29 & 20.82 \\
		\hline
	\end{tabular}
	\vspace{0.5em}
	\caption{Possible NEWSOLAR Connections with Line Costs (M\$)}
	\label{tab:all_conn}
\end{table}

We found that simply installing connections to BUCKEYE and APPLE results in several contingency violations. These violations came from over-currents on the OAK-BUCKEYE line we so we replaced that line with Crow conductors to ensure ample allowance for current. With the replaced line we saw no violations. The total cost for case 1 with this upgrade is shown in Table \ref{tab:cost_breakdown_case1}.
\begin{table}[h!]
	\centering
	\begin{tabular}{|l|r|}
		\hline
		\textbf{Modification} & \textbf{Cost (M\$)} \\ \hline
		\multicolumn{2}{|l|}{\textbf{Replace OAK-BUCKEYE (69kV Crow)}} \\ 
		\hspace{1em} Fixed Cost & 0.75 \\ 
		\hspace{1em} Variable Cost (\$390,000/km for 8 km) & 3.12 \\ 
		\hspace{1em} \textbf{Total} & \textbf{3.87} \\ \hline
		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-BUCKEYE (69kV Rook)}} \\ 
		\hspace{1em} Fixed Cost & 0.75 \\ 
		\hspace{1em} Variable Cost (\$370,000/km for 6 km) & 2.22 \\ 
		\hspace{1em} \textbf{Total} & \textbf{2.97} \\ \hline
		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-APPLE (69kV Rook)}} \\ 
		\hspace{1em} Fixed Cost & 0.75 \\ 
		\hspace{1em} Variable Cost (\$370,000/km for 6 km) & 2.22 \\ 
		\hspace{1em} \textbf{Total} & \textbf{2.97} \\ \hline
		\textbf{Grand Total} & \textbf{9.81} \\ \hline
	\end{tabular}
	\vspace{0.5em}
	\caption{Cost Breakdown for Case 1 Implementation with OAK-BUCKEYE Upgrade}
	\label{tab:cost_breakdown_case1}
\end{table}

This cost exceeds that of cases 2, 4, 6, 8, 10 and 11 as seen in Table \ref{tab:all_conn}. However, the cheapest 6km installation costs \$3M, so for any of these other cases to be preferred there must be no contingency violations. If there are, any corrective line replacement will make that option more expensive than case 1 with upgrade.

\section{Conclusion}
Summary of key findings and recommendations
\end{document}
